Supporting Information: Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2020-01-08 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Condensing

  \section{Mean first passage time simulations}\label{section:mfpt}

%  We validated our approach to simulating trajectory realizations by testing
%  it against analytical solutions to the mean first passage time of a Brownian
%  particle with 2 absorbing boundaries.
  \subsection*{Analytical fits to MFPT distributions}

@@

>>>>

  \section*{Analytical fits to MFPT distributions}\label{section:mfpt_fits}

@@

  \section{Explanation of Under-Estimated MSDDM $\beta$ Values}\label{section:beta_estimates}

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.43\textwidth}
  \includegraphics[width=\textwidth]{beta_hurst.pdf}
  \caption{}\label{fig:beta_hurst}
  \end{subfigure}
  \begin{subfigure}{0.52\textwidth}
  \includegraphics[width=\textwidth]{beta_parameters.pdf}
  \caption{}\label{fig:beta_parameters}
  \end{subfigure}
  %BJC5: need to update MSDDM (immobile states). Waiting on those simulations
  %MRS6: should try to lead with what the overall results/conclusions are.  What does it mean that parameters are larger or smaller?  What should the reader take from the discussion?  Should it be in supportinig?
  \caption{(a) The $\beta$ values of the sFBMcut model appear to be inversely proportional
  to the Hurst parameters. The $\beta$ values of the MSDDM are much lower with much less
  variation than the sFBMcut model. (b) The $\beta$ parameters of the MSDDM are low because
  sub-trajectories between state transitions decorrelate transitional hops and because
  our FLM simulation procedure does not accurately correlate hops after long time lags. 
  The high $\beta$ parameters of the sFBMcut model are a consequence of anti-correlation
  between hops. Removing hop correlations causes $\beta$ to drop down close to MSDDM
  values (sFBMcut ($H$=0.5)). Removing dwell times in addition to hop correlation
  yields a similar value of $\beta$ (Brownian). Immobilizing particles while in a trapped state
  also yields a similar value of $\beta$ (MSDDM (immobile states)). Replacing FLM with
  FBM in the MSDDM raises $\beta$ well above the Brownian value (MSDDM (FBM)). Replacing FLM with FBM and
  immobilizing particles in trapped states further raises the value of $\beta$.}\label{fig:beta}
  \end{figure}
